---
title: "space_launch_viz"
author: "kimmy wong"
format: html
editor_options: 
  chunk_output_type: console
---
```{r}
library(tidyverse)
library(here)
library(janitor)
library(paletteer)
library(ggrepel)
library(gghighlight)
```

```{r}
space_launch <- read_csv(here("data", "space_launches.csv"))
```

```{r}
ggplot(data = space_launch, aes(x = launch_year, y = agency)) +
  geom_violin(color = "green") +
  theme(plot.background = element_rect(fill = "pink"),
  panel.background = element_rect(fill = "cadetblue3", color = "orange"),
  panel.grid.major = element_line(color = "red"),
  text = element_text(size = 12, family = "serif")) +
  annotate("text",
           x = 1970,
           y = "SEALP",
           label ="W0Ww00OWoooo ROCkeTs",
           color = "purple") +
  annotate("text",
           x = 2000,
           y = "LMA",
           label ="moooorreee rOCkeTsssss",
           color = "purple") +
  labs(x = "YeAr",
       y = "aGeNCy",
       title = "rocektss in space") +
  scale_x_continuous(limits = c(1960, 2020), 
                     expand = c(0,0),
                     breaks = seq(1960, 2020, by = 1))
  

            
      